Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-11 paper-plan/paper-plan.tex
Some papers
Stupidly simple outline, without real content yet :)

>>>>

\section{Motivation}

There is some domain in which requires probabilistic planning. As FF-Replan and
RFF are about using deterministic planners in a probabilistic domain, we like
to see what's new and if we can find some holes that are still open.

\section{Literature Summaries}

\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}

Graphplan is a successful planning algorithm for classical STRIPS domains. This
paper explores the extend it can be used in \emph{probabilistic} domains. The
paper discusses two variations of Graphplan: PGraphplan and TGraphplan.
PGraphplan produces an optimal plan, while TGraphplan produces a sub-optimal
plan but it has increased speed. By comparing the speed and quality of the
two planners the authors are able to estimate how far they are from the ideal.

\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013compiling}}

\section{Conclusion from Literature and problem statement}

From the related literature we identify some problems.

\section{Solution for the problem}

We try to find some solution or direction how to solve the problem

\section{Conclusion}

Did it work.

\section{More Literature}

\begin{itemize}
	\item \cite{Hoffmann01theff}
	\item \cite{FFReplan}
	\item \cite{teichteil2010incremental}
	\item \cite{yoon2008probabilistic}
	\item \cite{teichteil2012fast}
	\item \cite{bonet2011planning}
\end{itemize}
